Catastrophic Goodhart: regularizing RLHF with KL divergence does not mitigate heavy-tailed reward misspecification

### 2024-10-25 paper/main.tex
minor wording change
added acknowledgement

@@

Results are in figure \ref{fig:ppo}. Midway through training, the model generates reasonable completions with a higher number of "the" tokens than usual, but as training progresses the model starts to generate completions with a very high number of "the" tokens while proxy reward reaches values $>10^9$, demonstrating that the basic pattern of catastrophic Goodhart can occur in RLHF under conditions of heavy-tailed error.

>>>>

\begin{ack}
This work was supported by the Long-Term Future Fund (LTFF). We also thank the anonymous reviewers for their valuable feedback and constructive suggestions. 
\end{ack}

@@

Two example completions are in figure \ref{fig:ppo}. Midway through training, the model generates reasonable text with a higher number of "the" tokens than usual, but as training progresses the model starts to generate completions with a very high number of "the" tokens while proxy reward reaches values $>10^9$, demonstrating that the basic pattern of catastrophic Goodhart can occur in RLHF under conditions of heavy-tailed error.
